When and Where: Examining Crisis Service Calls in Toronto

### 2024-09-24 paper/paper.qmd
Updated README and plots in paper

library(tidyverse)
library(ggplot2)
```

@@

```{r}
data <- read.csv("../data/analysis_data/piccfsa.csv")
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
#| 
ggplot(data, aes(x = event_dow, fill = event_type)) + 
  geom_bar(position = "dodge") + 
  labs(title = "Event Type Counts Grouped by Day of the Week", 
       x = "Day of the Week", 
       y = "Count",
       fill = "Event Type") +
  theme_minimal()
```

```{r}
ggplot(data, aes(x = event_month, fill = event_type)) + 
  geom_bar(position = "dodge") + 
  labs(title = "Event Type Counts Grouped by Day of the Week", 
       x = "Day of the Week", 
       y = "Count",
       fill = "Event Type") +
  theme_minimal() +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

```{r}
df_summarized <- data %>%
  group_by(event_hour, event_type) %>%
  summarise(count = n()) %>%
  ungroup()

@@

```{r}
library(cowplot)  # For combining plots

# Step 1: Summarize the data by counting occurrences of each event_type
df_summarized <- data %>%
  group_by(hood_158, event_type) %>%
  summarise(count = n()) %>%
  ungroup()

@@

# Create a list to hold the top 10 data frames and plots
df_list <- list()
plot_list <- list()

@@

  # Save the data frame to the list
  df_list[[event]] <- df_top10

@@

# Step 4: Get a look-up table
neighborhood_table <- data %>%
  select(hood_158, neighbourhood_158) %>%
  distinct() %>%
  arrange(hood_158)

# Convert the table to a grid object using gridExtra::tableGrob
table_plot <- gridExtra::tableGrob(neighborhood_table)

# Step 5: Combine the individual plots using cowplot
combined_plot <- cowplot::plot_grid(plotlist = plot_list, ncol = 1)

# Step 6: Display the combined plot
print(combined_plot)
```

>>>>

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(cowplot)
```

@@

```{r}
#| include: false
#| warning: false
#| message: false
data <- read.csv("../data/analysis_data/piccfsa.csv")
```

@@

```{r}
#| label: fig-dow
#| fig-cap: Event Type Counts Grouped by Day of the Week
#| echo: false
#| warning: false
#| message: false
ggplot(data, aes(x = event_dow, fill = event_type)) + 
  geom_bar(position = "dodge") + 
  labs(title = "Event Type Counts Grouped by Day of the Week", 
       x = "Day of the Week", 
       y = "Count",
       fill = "Event Type") +
  theme_minimal()
```

```{r}
#| label: fig-month
#| fig-cap: Event Type Counts Grouped by the Month
#| echo: false
#| warning: false
#| message: false
ggplot(data, aes(x = event_month, fill = event_type)) + 
  geom_bar(position = "dodge") + 
  labs(title = "Event Type Counts Grouped by the Month", 
       x = "Month", 
       y = "Count",
       fill = "Event Type") +
  theme_minimal() +
  coord_flip()
```

```{r}
#| label: fig-year
#| fig-cap: Event Type Counts Grouped by Year
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-hour
#| fig-cap: Event Type Counts Grouped by Hour of the Day
#| echo: false
#| warning: false
#| message: false
df_summarized <- data %>%
  group_by(event_hour, event_type) %>%
  summarise(count = n()) %>%
  ungroup()

@@

```{r}
#| label: fig-date
#| fig-cap: Event Type Counts Grouped by Date
#| echo: false
#| warning: false
#| message: false
df_summarized <- data %>%
  group_by(event_date, event_type) %>%
  summarise(count = n()) %>%
  ungroup()

# Create the line plot
ggplot(df_summarized, aes(x = event_date, y = count, color = event_type, group = event_type)) + 
  geom_smooth() + 
  labs(title = "Event Type Counts Grouped by Date", 
       x = "Date", 
       y = "Count", 
       color = "Event Type") +
  theme_minimal()
```

```{r}
#| label: fig-hood
#| fig-cap: Event Counts in Neighbourhood Grouped by Event Type
#| echo: false
#| warning: false
#| message: false
# Step 1: Summarize the data by counting occurrences of each event_type
df_summarized <- data %>%
  group_by(hood_158, event_type) %>%
  summarise(count = n()) %>%
  ungroup()

@@

# Create a list to hold the top 10 data frames and plots
df_list <- list()
plot_list <- list()
hood_list <- c()

@@

  # Save the data frame to the list
  df_list[[event]] <- df_top10
  hood_list <- c(hood_list, df_top10$hood_158)

@@

# Step 4: Combine the individual plots using cowplot
combined_plot <- cowplot::plot_grid(plotlist = plot_list, ncol = 3)

# Step 5: Display the combined plot
print(combined_plot)
```

```{r}
#| label: tab_hood
#| fig-cap: A Look-up Table for Hood Number and Hood Name
#| echo: false
#| warning: false
#| message: false
# Step: Get a look-up table
hood_set <- unique(hood_list)
neighborhood_table <- data %>%
  select(hood_158, neighbourhood_158) %>%
  distinct() %>%
  filter(hood_158 %in% hood_set) %>%
  arrange(hood_158) %>%
  rename("hood number" = hood_158,  
         "hood name" = neighbourhood_158)

grid.arrange(grid.table(neighborhood_table))
```
